|

### 2020-04-03 draft-master/inst/rmarkdown/templates/jop/skeleton/JOPskeleton.Rmd
Includes submitted JOPskeleton

---
title: | 
  | Campaign Contribution Limits and Corruption 
  | Evidence from the 50 states
author: "Mark C. Hand"
date: ""
output: pdf_document
header-includes:
- \usepackage{pdflscape}
- \newcommand{\blandscape}{\begin{landscape}}
- \newcommand{\elandscape}{\end{landscape}}
- \usepackage{setspace}
- \doublespacing
---

Since the 1970s, the U.S. Supreme Court has maintained that nearly all limits on political spending violate the first amendment’s protection of free speech. In its 1976 _Buckley v. Valeo_ decision, the Court laid out only two admissible justifications for limiting campaign donations: To prevent corruption or the appearance of corruption. But do campaign finance limits actually prevent corruption or its appearance? As current challenges to contribution limits wind their way through federal courts, the answer to this question will inform the Supreme Court’s decision to uphold or strike down remaining limits on political campaign contributions. Using state-level data from 1990-2012 on contribution limits, corruption convictions, and media mentions of corruption, this paper employs linear panel regressio to test whether campaign contribution limits are associated with lower levels of corruption convictions or media mentions of corruption. These methods find associations between corruption convictions and the presence of limits on donations to political action committees (PACs), the amount of those limits, and the presence of limits on donations to parties; individual donation limits do not prove associated with either measure of corruption.[^SPSA]

[^SPSA]: An earlier version of this paper was presented at the Annual Meeting of the Southern Political Science Association in January 2019. Analyses available on [GitHub](https://github.com/markchand/Money-in-Politics).

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = FALSE, eval=FALSE, cache = TRUE, message=FALSE, warning=FALSE)
library(haven) # import .dta
library (MASS) # For binomial regression 
library(tidyverse) # everything; placed here because of MASS::select() overlap 
library(plm) # For linear panel regression
library(stargazer) # For regression outputs #fail 
library(knitr) # Because Matt Worthington said so 
library(pglm) # For panel + binomial 
library(webshot) # For screenshots 
library(viridis) # For colorblindedness
library(GGally) # For ggpairs
library(lm.beta) # For standardized regression coefficients 
library(broom) # for augment()
theme_set(theme_classic()) # Sets default theme

@@

```{r data import, eval=T, message=F, warning=F}
# Alt and Lassen's "Enforcement and Public Corruption: Evidence from US States" 
# http://epstein.wustl.edu/research/LPE.Alt.pdf
AltLassen <- read_dta("data/Replication/AltLassenJLEO.dta")

@@

##Introduction
In 1976, the Supreme Court ruled in _Buckley v. Valeo_ that political campaign expenditures are the equivalent of free speech, and therefore protected by the first amendment. At the same time, the Court laid out one mechanism and two permissible reasons for limiting campaign contributions that enable those expenditures. First, it argued that more money contributed does not amount to “more” speech, allowing for the use of campaign contribution dollar amount limits. Donating one dollar or $5,000 to a political campaign amounts to a speech act, the Court held, and so it is permissible to impose limits on the amount of contributions as long as contributions are not prevented. Second, having laid out this mechanism by which money in politics might be limited, the court laid out only two constitutionally permissible reasons for limiting contributions: To prevent corruption or the appearance thereof. As Kang (2012) argues, the holdings in _Buckley v. Valeo_ provided “the basic framework of contribution limits and disclosure requirements” for the following four decades. Since _Buckley v. Valeo_, Congress has passed only one campaign finance law, the Bipartisan Campaign Reform Act of 2002. Better know as McCain-Feingold, the bill took aim at unlimited “soft money” contributions to political parties and expanded the Federal Election Commission’s disclosure requirements to what it called “electioneering communications,” political ads not paid for by campaigns themselves.

@@

##Prior Work 
Since the Buckley v. Valeo decision, a wave of scholarship has taken advantage of the campaign contribution data collected by the Federal Election Commission to examine the causes and consequences of political campaign contributions, including whether contributions buy access (not to a meaningful degree, find Welch 1982 and Langbein 1986) and the effectiveness of contributions relative to lobbying efforts (yes, according to Wright 1990). Since the 2010 Citizens United and speechnow.org decisions, another arm of scholarship has examined the flows of money to groups engaging in independent expenditures (Spencer and Wood 2014, Werner and Coleman 2014).

@@

##Data and Design  
In this paper, I build upon the growing body of state-level political science research to ask whether campaign contribution limits at the state level associated with lower levels of corruption. Given open debate about the proper measure of state-level corruption, I use two measures. The first, a Corruptions Convictions Index, is the traditional measure of state level corruption, built from Department of Justice convictions data. The second, the Corruptions Reflection Index, is a new measure put forward by Dincer and Johnston (2016). I combine these measures with a third data set from Michael Barber’s 2016 work on campaign contribution limits and political polarization; and a fourth data set from James Alt and David Dryer Lassen, to provide controls for the full model (Alt and Lassen 2012).

@@

##Results 
The results of the panel regressions reveal multiple correlations between state-level campaign limits and Corruption Convictions; and one correlation between those limits and the Corruption Reflections Index.

@@

\newpage
## Appendix A: Descriptions and Descriptive Statistics of Control Variables 
In their 2012 paper "Enforcement and Public Corruption: Evidence from the American States," Glaeser and Saks make use of the following control variables, which we have included here:

@@

\newpage
## References 
<!--Add new authors (see Google doc) and data. R packages?-->
Ansolabehere, Stephen, John M de Figueiredo, and James M Snyder Jr. 2003. “Why is there so Little Money in US Politics?” Journal of Economic Perspectives. 17(1): 105–130.

@@

```{r CRI heteroskedasticity checks,include=F}
AltBarber2 <- AltBarber %>% drop_na()

cri.log.iv2 <- plm(log(CRI+1) ~ 
             ind_limits_2010*ind_limits_dummy 
           + ind2pty_limits_2010*ind2pty_limits_dummy 
           + pac_limits_2010*pac_limits_dummy
           + eopop # AUSAs per million population
           + citi6006 # Citizen ideology measure 
           + high_school + # Percent high school graduates
           + rgenrevpc # Real per capita gov revenues ($1000)
           + men_ineqincwag # Inequality: Male wages
           + urbanization_2 # Urbanization 
           + logpop, # Log of population (millions)
           data = AltBarber2, 
           model="pooling")

# https://towardsdatascience.com/linear-and-bayesian-modelling-in-r-predicting-movie-popularity-6c8ef0a44184

# Each numerical explanatory variable is linearly related to the response variable
ggplot(augment(cri.log.iv2), aes(x = (AltBarber2$pac_limits_2010*AltBarber2$pac_limits_dummy), y = .resid))+
 geom_point(colour = "red", size = 2, alpha = 0.5)+
 theme_classic()+
 geom_smooth(se=FALSE)+
 labs(x = "?", y= "residuals")+
 geom_hline(yintercept = 0, linetype = "dashed")

# Residuals are distributed nearly normal with a mean of 0 
par(mfrow=c(1,2))
hist(cri.log.iv2$residuals, main = "Residual Distribution", 
 xlab = "Residuals", col = "lightgreen")
qqnorm(cri.log.iv2$residuals, col = "blue")
qqline(cri.log.iv2$residuals, col = "red")

# Variability of residuals is nearly constant 
ggplot(augment(cri.log.iv2), aes(x= .fitted, y= .resid))+
 geom_point(colour = "blue", size = 2, alpha = 0.5)+
 theme_classic()+
 geom_smooth()+
 geom_hline(yintercept = 0, linetype = "dashed")+
 labs(x = "Fitted", y = "Residuals")

# The residuals are independant 
ggplot(augment(cri.log.iv2), aes(x = seq_along(.resid), y = .resid)) + 
 geom_point(colour = "lightgreen", size = 2.5, alpha = 0.6)+
 theme_classic()+
 labs(x = "Order of Collection", y = "Residuals", title = "Residuals vs. Order of Collection")

# Do this for the other two independent variable pairs? 
```

```{r CCI Standardized coefficients,eval=T,include=F}
# https://stackoverflow.com/questions/42076903/including-standardized-coefficients-in-a-stargazer-table
cci.log.iv.lm <- lm(log(CCI+1) ~ 
           ind_limits_2010*ind_limits_dummy 
           + ind2pty_limits_2010*ind2pty_limits_dummy 
           + pac_limits_2010*pac_limits_dummy
           + jdiv  # Divided government 
           # + bindingonetermlimit # Binding one-term limit 
           # + bindingtwotermlimit # Binding two-term limit 
           # + rpcinc_annual_new # Real per capita income ($1000)
           + eopop # AUSAs per million population
           # + unemp # Unemployment 
           # + citi6006 # Citizen ideology measure 
           + high_school + # Percent high school graduates
           + rgenrevpc # Real per capita gov revenues ($1000)
           # + men_ineqincwag # Inequality: Male wages
           # + grelimp # Relative government wages
           + urbanization_2 # Urbanization 
           + logpop, # Log of population (millions)
           data=AltBarber)

cci.beta <- lm.beta(cci.log.iv.lm)
```

```{r CCI standardized coefficients,eval=T,results="asis",include=F}
stargazer(
  #cri.log.iv,
  cci.log.iv.lm,
  cci.beta,
  type="latex",
  coef = list(
    cci.log.iv.lm$coefficients,
    cci.beta$standardized.coefficients),
  header=F,
  font.size = "small")
```

```{r CRI Standardized coefficients,eval=T,include=F}
# https://stackoverflow.com/questions/42076903/including-standardized-coefficients-in-a-stargazer-table
cri.log.iv.lm <- lm(log(CRI+1) ~ 
             ind_limits_2010*ind_limits_dummy 
           + ind2pty_limits_2010*ind2pty_limits_dummy 
           + pac_limits_2010*pac_limits_dummy
           # jdiv  # Divided government 
           # + bindingonetermlimit # Binding one-term limit 
           # + bindingtwotermlimit # Binding two-term limit 
           # + rpcinc_annual_new # Real per capita income ($1000)
           + eopop # AUSAs per million population
           # + unemp # Unemployment 
           + citi6006 # Citizen ideology measure 
           + high_school + # Percent high school graduates
           + rgenrevpc # Real per capita gov revenues ($1000)
           + men_ineqincwag # Inequality: Male wages
           # + grelimp # Relative government wages
           + urbanization_2 # Urbanization 
           + logpop, # Log of population (millions)
           data = AltBarber)

cri.beta <- lm.beta(cri.log.iv.lm)

# What in the world does any of *this* mean? It generates a bunch of stars on each standardized coefficient, which seems unlikely. 
```

```{r CRI standardized coefficients,eval=T,results="asis", include=F}
stargazer(
  #cri.log.iv,
  cri.log.iv.lm,
  cri.beta,
  type="latex",
  coef = list(
    cri.log.iv.lm$coefficients,
    cri.beta$standardized.coefficients),
  header = F,
  font.size = "small")
```

>>>>

---
title: | 
  | Campaign Contribution Limits and Corruption 
  | Evidence from the 50 states
author: "Mark Hand"
abstract: "Since its 1976 _Buckley v. Valeo_ decision, the Supreme Court has allowed only two potential justifications for limiting campaign donations: To prevent corruption or the appearance of corruption. Do campaign finance limits actually mitigate corruption or its appearance? As current challenges to contribution limits wind their way through federal courts, the answer to this question will inform the  Supreme Court’s decision to uphold or strike down remaining limits on political campaign contributions. Using state-level data from 1990-2012 on contribution limits, corruption convictions, and media mentions of corruption, this paper finds associations between corruption convictions and the presence of limits on donations to political action committees (PACs), the amount of those limits, and the presence of limits on donations to parties. Individual donation limits, however, do not prove associated with either measure of corruption."
anonymized: true
output:
    draft::jop_submission:
        keep_tex: yes
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = FALSE, eval=FALSE, cache = TRUE, message=FALSE, warning=FALSE)
library(haven) # import .dta
library(MASS) # For binomial regression 
library(tidyverse) # everything; placed here because of MASS::select() overlap 
library(plm) # For linear panel regression
library(stargazer) # For regression outputs #fail 
library(knitr) # Because Matt Worthington said so 
library(pglm) # For panel + binomial 
library(webshot) # For screenshots 
library(viridis) # For colorblindedness
library(GGally) # For ggpairs
library(lm.beta) # For standardized regression coefficients 
library(broom) # for augment()
library(devtools) # For downloading packages from github 
install_github("duckmayr/draft") # For JOP template 
theme_set(theme_classic()) # Sets default theme

@@

```{r data import, eval=T, message=F, warning=F}
# Alt and Lassen's "Enforcement and Public Corruption: Evidence from US States" 
# http://epstein.wustl.edu/research/LPE.Alt.pdf
AltLassen <- read_dta("~/Documents/GitHub/Money-in-Politics/data/Replication/AltLassenJLEO.dta")

@@

## Introduction
In 1976, the Supreme Court ruled in _Buckley v. Valeo_ that political campaign expenditures are the equivalent of free speech, and therefore protected by the first amendment. At the same time, the Court laid out one mechanism and two permissible reasons for limiting campaign contributions that enable those expenditures. First, it argued that more money contributed does not amount to “more” speech, allowing for the use of campaign contribution dollar amount limits. Donating one dollar or $5,000 to a political campaign amounts to a speech act, the Court held, and so it is permissible to impose limits on the amount of contributions as long as contributions are not prevented. Second, having laid out this mechanism by which money in politics might be limited, the court laid out only two constitutionally permissible reasons for limiting contributions: To prevent corruption or the appearance thereof. As Kang (2012) argues, the holdings in _Buckley v. Valeo_ provided “the basic framework of contribution limits and disclosure requirements” for the following four decades. Since _Buckley v. Valeo_, Congress has passed only one campaign finance law, the Bipartisan Campaign Reform Act of 2002. Better know as McCain-Feingold, the bill took aim at unlimited “soft money” contributions to political parties and expanded the Federal Election Commission’s disclosure requirements to what it called “electioneering communications,” political ads not paid for by campaigns themselves.

@@

## Prior Work 
Since the Buckley v. Valeo decision, a wave of scholarship has taken advantage of the campaign contribution data collected by the Federal Election Commission to examine the causes and consequences of political campaign contributions, including whether contributions buy access (not to a meaningful degree, find Welch 1982 and Langbein 1986) and the effectiveness of contributions relative to lobbying efforts (yes, according to Wright 1990). Since the 2010 Citizens United and speechnow.org decisions, another arm of scholarship has examined the flows of money to groups engaging in independent expenditures (Spencer and Wood 2014, Werner and Coleman 2014).

@@

## Data and Design  
In this paper, I build upon the growing body of state-level political science research to ask whether campaign contribution limits at the state level associated with lower levels of corruption. Given open debate about the proper measure of state-level corruption, I use two measures. The first, a Corruptions Convictions Index, is the traditional measure of state level corruption, built from Department of Justice convictions data. The second, the Corruptions Reflection Index, is a new measure put forward by Dincer and Johnston (2016). I combine these measures with a third data set from Michael Barber’s 2016 work on campaign contribution limits and political polarization; and a fourth data set from James Alt and David Dryer Lassen, to provide controls for the full model (Alt and Lassen 2012).

@@

## Results 
The results of the panel regressions reveal multiple correlations between state-level campaign limits and Corruption Convictions; and one correlation between those limits and the Corruption Reflections Index.

@@

## Appendix A: Descriptions and Descriptive Statistics of Control Variables 
In their 2012 paper "Enforcement and Public Corruption: Evidence from the American States," Glaeser and Saks make use of the following control variables, which we have included here:

@@

## References 
<!--Add new authors (see Google doc) and data. R packages?-->
Ansolabehere, Stephen, John M de Figueiredo, and James M Snyder Jr. 2003. “Why is there so Little Money in US Politics?” Journal of Economic Perspectives. 17(1): 105–130.

@@

<!-- As instructed by Noorah:  
rmarkdown::render("/Users/markchand/Documents/GitHub/Money-in-Politics/draft-master/inst/rmarkdown/templates/jop/skeleton/JOPskeleton.Rmd", output_format="latex_document") -->
